Processing Code

### 2023-04-06 code/processing_code/processingcode.qmd
Part 4

---
title: "Processing Code for September Data"
output: 
  html_document
---

# Processing 1

@@

## Cleaning

@@

@@

# Processing 2

@@

# Cleaning is done, now lets save the processed data

@@

# Processing 3

@@

# Processing 4

@@

# Processing script 5

@@

# Processing 6

@@

>>>>

---
title: "Processing Code"
output: 
  html_document
---

# Processing Section for Vaccination Data in Albany, GA

## Processing 1: Getting Vaccination Totals by Target Zips 31701, 31705 & 31707 for the Month of September

@@

@@

### Filtering the data by zip code

@@

## Processing 2: Getting Vaccination Totals by Target Zips 31701, 31705 & 31707 for the Month of October

@@

 is done, now lets save the processed data

@@

## Processing 3: : Getting Vaccination Totals by Target Zips 31701, 31705 & 31707 for the Month of November

@@

## Processing 4: Getting Vaccination Totals by Target Zips 31701, 31705 & 31707 for the Month of December

@@

## Processing 5: Getting Vaccination Totals by Target Zips 31701, 31705 & 31707 for the Month of January

@@

## Processing 6: : Getting Vaccination Totals by Target Zips 31701, 31705 & 31707 for the Month of February

@@

# Processing for Vaccination Data for Our Control Richmond County

## Processing 1: Getting Vaccination Totals by Control Zip 31701
